\section{Hyperpartisan Fake News Styles}
\label{sec:hyperpartisan_fake_news_styles}

\citet{potthast_stylometric_2018} presented using the unmasking approach, traditionally used for distinguishing author styles, 
to distinguish between genres (i.e., hyperpartisan and non-hyperpartisan news articles). 

There are different categories of fake news detection mechanisms, such as knownledge-based (by relating to known facts), 
context-based (by analysing news spread in social media), and style-based (by analysing writing style).

\citet{potthast_stylometric_2018} discard hardly represented features, such as word tokens that occur in less than $2.5 \%$ of the documents, 
and n-gram features that occur in less than $10 \%$ of the documents.
Otherwise, the model could overfit and could not generalize well to unseen data.

To avoid biases from datasets, they balance the training set by oversampling.

They use WEKA's random forest implementation.
Their code is publicly available (cf. \citep{potthast_stylometric_2018}). 

Satire is form of fake news, but its purpose is to entertain.

\subsection{Topic features for satire classification}
\label{sec:topic_features_for_sarcasm_classification}

\citet{potthast_stylometric_2018} argue that topic features are not appropriate for satire classification, 
since topics of satire change along the topics of news and thus, a classifier with topic features does not generalize.

\subsection{Generalizing unmasking to genre detection}
\label{sec:generalizing_unmasking_to_genre_detection}

\citet{potthast_stylometric_2018} omit the first step of the unmasking approach, i.e., chunking texts to create multiple text instances for the curve.
Instead, texts of possibly different genres but in the same genre are considered as belonging to the same class.
The documents of two genres are used as input to the classifier.
As usual, steeper decreases in classification error curves indicate higher style similarity of the two input documents.