\section{Tasks}
\label{sec:tasks}

In this section we outline the main tasks of authorship analysis. 
We begin with the foundational problems of \ac{aa} and \ac{av}, before turning to derivative tasks such as \ac{llm} detection.

\subsection{Authorship Attribution}
\ac{aa} is the classical multi-class, single-label text classification task in which, given a set of candidate authors $A$ with known texts $K=\bigcup_{a\in A} K_a$, where $K_a$ denotes the set of texts known to be authored by author $a$, the goal is to determine which author wrote a disputed text $d \in U$, where $U$ is the set of texts of unknown authorship~\citep{koppel_authorship_2004,barlas_cross_domain_2020}. 
Here, $k_a$ denotes a single text known to be authored by $a$.
In the closed-set setting, each $d \in U$ must be attributed to exactly one $a \in A$. 
Cross-topic and cross-genre \ac{aa} introduce distributional shifts between training and test data, complicating the task~\citep{barlas_cross_domain_2020}.
Formally, \ac{aa} aims to learn the function $f_{AA}: U \to A, d \mapsto a \text{, where } a \in A$.


\subsection{Authorship Verification}
\ac{av} addresses the problem of establishing whether a given text $d \in U$ was written by a candidate author $a \in A$, using a set of the author’s known writings $K_a$ as reference~\citep{koppel_authorship_2004}.
We denote disputed-candidate pair the input of the text of unknown authorship $d$ and the candidate author's text $k_a \in K_a$ in the following.
In contrast to \ac{aa}, \ac{av} does not have reliable negative examples, since assembling a representative sample of all texts not authored by 
$a$ is impossible. 
This limitation makes \ac{av} a more challenging classification problem than \ac{aa}~\citep{llm_detection_av_2025,neal_surveying_2018,koppel_authorship_2004}.
\ac{av} is framed as a one-class, a binary, or a similarity detection task depending on the methodological perspective~\citep{neal_surveying_2018,koppel_authorship_2004}.  
We consider \ac{av} a one-class classification task.
\ac{aa} can be reduced to a series of \ac{av} problems, where the other direction is typically not true~\citep{barlas_cross_domain_2020,tyo_state_2022}.
We formalize \ac{av} as $f_{\text{AV}} : U \times K \to \{0,1\}, \quad
(d, k_a) \mapsto 
\begin{cases} 
1, & \text{if } d \text{ was authored by } a,\\
0, & \text{otherwise.}
\end{cases}
$
% Gespräch Martin Potthast 19.05.2025: problem formulation 2 is less common and in the context of very sparse (metadata) information:
% This task can also be formulated as whether two texts $t_1$ and $t_2$ are written by the same author 
% \citep{bevendorff_generalizing_2019,bevendorff_divergence_based_2020,embarcadero_ruiz_graph_based_2022,rivera_soto_learning_2021,ordonez_will_2020,futrzynski_pairwise_2021,weerasinghe_feature_vector_difference_2021,llm_detection_av_2025}.


% \subsection{Author Profiling}
% Author profiling infers sociolinguistic attributes of an author, such as age, gender, education, or mental health, from a set of texts. 
% It is grounded in the assumption that subconscious idiosyncrasies of writing style encode personal traits~\citep{emmery_adversarial_2021,stamatatos_survey_2009,elmanarelbouanani_authorship_2014}. 
% Profiling raises substantial ethical and privacy concerns due to the sensitivity of the inferred attributes.

% \subsection{Author Obfuscation}
% Author obfuscation is an adversarial task in which a text is deliberately modified to conceal the author's identity while preserving its semantic content. 
% It directly opposes \ac{aa} and \ac{av} by aiming to neutralize stylometric features~\citep{bischoff_importance_2020,bevendorff_divergence_based_2020,gohsen_task_oriented_2024}. 

% \subsection{Intrinsic Plagiarism Detection}   % style change detection
% Plagiarism detection is the task of identifying reused or unattributed content in texts~\citep{stein_intrinsic_2011,gohsen_task_oriented_2024}. 
% Unlike \ac{aa}, the goal is not to establish authorship but to uncover overlap between documents, regardless of author identity~\citep{elmanarelbouanani_authorship_2014}.
% Hence, plagiarism detection is an application of \ac{av}~\citep{rivera_soto_learning_2021}.


\subsection{\acs{llm} Detection}
Given their ability to generate human-like text, \acp{llm} can be conceptualised as one or multiple distinct authors. 
Due to the diversity of \acp{llm}, treating them as a single author may be misleading, motivating distinct authorships for different models. 
This framing allows \ac{llm} detection to be cast as an \ac{av} task where given two texts, one of unknown authorship and one known to be generated by an \ac{llm}, the goal is to determine whether they share the same author~\citep{llm_detection_av_2025}.


